---
title: "RMLQ2"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "figure/")
```
Loading the libraries needed
```{r message=FALSE, warning=FALSE}
library(caret); library(rpart); library(ggplot2); library(rattle);
library(AppliedPredictiveModeling); library(ElemStatLearn); library(pgmm);

data(segmentationOriginal)
df <- data.frame(segmentationOriginal)
#summary(df)
## subset data into training and test sets
training<-df[which(df$Case=='Train'),]
testing <-df[which(df$Case=='Test'),]
set.seed(125)
modFit <- train(Class~., method="rpart", data=training)
print(modFit$finalModel)

fancyRpartPlot(modFit$finalModel)
#plot(modFit$finalModel,uniform=T,main="Classification Tree")
#text(modFit$finalModel,use.n=T, all=T,cex=0.8)
```


## Olive oil data
```{r oliveoil}
data("olive")
summary(olive)
```
Classification tree for the area:  
```{r olive_classification}
training <- as.data.frame(olive)
set.seed(125)
modFit <- train(Area~., method="rpart", data=training)
print(modFit$finalModel)
newdata = as.data.frame(t(colMeans(olive)))
head(newdata)
predict(modFit,newdata)
```
The result is not great, since it seems that the Area is being treated as a numeric data in this data frame even though it really is a factor variable.

## South Africa Heart Disease Data

```{r South-Africa-Heart-Disease-Data}
library(ElemStatLearn)
data(SAheart)
head(SAheart)
set.seed(8484)
train = sample(1:dim(SAheart)[1],size=dim(SAheart)[1]/2,replace=F)
trainSA = SAheart[train,]
testSA = SAheart[-train,]

set.seed(13234)

modFit <- train(chd~tobacco+ldl+typea+obesity+alcohol+age, family="binomial", method="glm", data = trainSA)
train_prediction <- predict(modFit,trainSA)
train_values <- trainSA$chd

test_prediction <- predict(modFit,testSA)
test_values <- testSA$chd

missClass = function(values,prediction){sum(((prediction > 0.5)*1) != values)/length(values)}
missClass(train_values,train_prediction)
missClass(test_values,test_prediction)
```

## The vowel data set

Load the sets from library ElemStatLearn and put them in two data frames:
```{r vowel sets}
data(vowel.train)
train<- as.data.frame(vowel.train)
data(vowel.test)
test<-as.data.frame(vowel.test)
```
Set the variable y to be a factor variable in both the training and test set. Then set the seed to 33833. Fit a random forest predictor relating the factor variable y to the remaining variables. 
```{r random-forest-predictor}
## Could use mutate but this is easier!
train$y<-as.factor(train$y)
test$y<-as.factor(test$y)
set.seed(33833)
modFit <- train(y~., data=train,method="rf",prox=T)
varImp(modFit)
```
